---
title: "R Notebook"
output: html_notebook
---

Loading Libraries

```{r}
library(dplyr)
library(tidyverse)
library(cowplot)
library(ggplot2)
library(grid)
library(gridExtra)
library(scales)
```

Load Data
```{r}
data <- read.csv("/Users/ks/Desktop/DDP/PREM/DATA_27APRIL2020/V1_allABCDDF.csv",header=T, na.strings=c("","[]","NA"))

```
Boxplot For Age distribution
```{r}
data$Gender <- as.factor(data$Gender)
data$Age..in.Months. <- as.integer(data$Age..in.Months.)
data %>% 
  filter(!is.na(Gender)) %>%
  filter(!is.na(Age..in.Months.)) %>%
  ggplot(aes(Age..in.Months. , fill = Gender)) + geom_boxplot() + coord_flip()
```

Removing Outliers
```{r}

for (i in 1:length(data$Age..in.Months.)){
    if(is.na(data$Age..in.Months.[i])|| data$Age..in.Months.[i] > 192) {
       (data$Age..in.Months.[i] = NA)
    }
  }
```



Preprocessing
```{r}
preprocessing <- function(df,red_cols) 
  { 
  # Removing duplicates
  df <- subset(df, duplicated(data[,15:col_length]) == FALSE)
  
  #Remove Redundant columns and Removing Empty ABCD, Etiology
  df <- df %>% 
        select(-c(redundant_cols)) %>%
        filter(!is.na(Airway) & !is.na(Breathing) & !is.na(Circulation) & !is.na(Disability)) %>%
        filter(!is.na(Etiology))
}
```

```{r}
redundant_cols <- c('X' , 'Unnamed..0' , 'No' , 'X_id' , 'form' , 'owner' , 'Type', 'createdOn', 'Patient.ID' , 'Patient.name', 'Unnamed..71')
col_length <- length(colnames(data))

data <- preprocessing(data, redundant_cols)
```

Distribution of Age Boxplot
```{r}
data$Gender <- as.factor(data$Gender)
data$Age..in.Months. <- as.integer(data$Age..in.Months.)
#df$Age..in.Months. <- df$Age..in.Months./12
age_box <- data %>% 
            filter(!is.na(Gender)) %>%
            filter(!is.na(Age..in.Months.)) %>%
            ggplot(aes(Age..in.Months. , fill = Gender)) + geom_boxplot() 
```

Age Distribution Density - Density plot
```{r}
age_density <- data %>% 
                filter(!is.na(Gender)) %>%
                filter(!is.na(Age..in.Months.)) %>%
                ggplot(aes(Age..in.Months. , fill = Gender)) + geom_density()

age_density

```

Combined Plot
```{r}
plot_grid(age_density, age_box, align = "v", nrow = 2, rel_heights = c(3/4,1/4))
```

Month wise distribution of patients
```{r}
#data$Month = as.factor(data$Month)
month_bar <- data %>% 
              filter(!is.na(Month)) %>%
              ggplot(aes(x = Month, y = ..count..)) + geom_bar()
 month_hist
```

District wise distribution of patients
```{r}
districts <- length(unique(data$District))
hospitals <- length(unique(data$hospital.name))
cat('Number of Districts: ', districts)
cat('\nNumber of Hospitals: ', hospitals)
district_bar <- data %>%
                  filter(!is.na(District)) %>%
                  ggplot(aes(x = District, y = ..count..)) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
district_bar
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

