---
title: "Binarised Dataset"
output: html_notebook
---

Load Libraries
```{r}
library(dplyr)
library(tidyverse)
library(qdapTools)
```

Load Data
```{r}
data <- read.csv("/Users/ks/Desktop/DDP/PREM/DATA_27APRIL2020/V1_allABCDDF.csv",header=T, na.strings=c("","[]","NA"))
```

Preprocessing
```{r}
source("preprocessing.R")
redundant_cols <- c('X' , 'Unnamed..0' , 'No' , 'X_id' , 'form' , 'owner' , 'Type', 'createdOn', 'Patient.ID' , 'Patient.name', 'Unnamed..71')
col_length <- length(colnames(data))

data <- basic_preproc(data, redundant_cols)
```

```{r}
disease_preproc <- function(df, red_cols){
  df <- df %>%
    select(-c(red_cols))
  
  #Etiology coloumns 52:81
  df <- df %>%
    mutate(Etiology = gsub("\\[|\\]", "", Etiology)) %>%
    mutate(Etiology = as.character(Etiology)) %>%
    mutate(Etiology = strsplit(Etiology, ","))
  etiology <<- colnames(mtabulate(df$Etiology))
  df <- cbind(df,mtabulate(df$Etiology))
  df <- df %>% select(-c("Etiology"," Breathlessness")) #Two columns formed with a space in between, hence remove it.
  
  df <- df %>%
    mutate(Cardiac = gsub("\\[|\\]", "", Cardiac)) %>%
    mutate(Cardiac = as.character(Cardiac)) %>%
    mutate(Cardiac = strsplit(Cardiac, ","))
  cardiac <<- colnames(mtabulate(df$Cardiac))
  df <- cbind(df,mtabulate(df$Cardiac))
  df <- df %>% select(-c("Cardiac","NO","Normal","NORMAL","-"))
  
  df <- df %>%
    mutate(Bronchodialators = gsub("\\[|\\]", "", Bronchodialators)) %>%
    mutate(Bronchodialators = as.character(Bronchodialators)) %>%
    mutate(Bronchodialators = strsplit(Bronchodialators, ","))
  bronchodialators <<- colnames(mtabulate(df$Bronchodialators))
  df <- cbind(df,mtabulate(df$Bronchodialators))
  df <- df %>% select(-c("Bronchodialators","NO","-","FALSE")) #Removin unecessary columns
  
  df <- df %>%
    mutate(Inotrope = gsub("\\[|\\]", "", Inotrope)) %>%
    mutate(Inotrope = as.character(Inotrope)) %>%
    mutate(Inotrope = strsplit(Inotrope, ","))
  inotrope <<- colnames(mtabulate(df$Inotrope))
  df <- cbind(df,mtabulate(df$Inotrope))
  df <- df %>% select(-c("Inotrope","-","NO","FALSE"))
  
  df <- df %>%
    mutate(Anti.Fit.Medication = gsub("\\[|\\]", "", Anti.Fit.Medication)) %>%
    mutate(Anti.Fit.Medication = as.character(Anti.Fit.Medication)) %>%
    mutate(Anti.Fit.Medication = strsplit(Anti.Fit.Medication, ","))
  anti.Fit.Medication <<- colnames(mtabulate(df$Anti.Fit.Medication))
  df <- cbind(df,mtabulate(df$Anti.Fit.Medication))
  df <- df %>% select(-c("Anti.Fit.Medication","-","NO","FALSE","TRUE")) 
  
  df <- df %>%
    mutate(Antibiotic = gsub("\\[|\\]", "", Antibiotic)) %>%
    mutate(Antibiotic = as.character(Antibiotic)) %>%
    mutate(Antibiotic = strsplit(Antibiotic, ","))
  antibiotic <<- colnames(mtabulate(df$Antibiotic))
  df <- cbind(df,mtabulate(df$Antibiotic))
  df <- df %>% select(-c("Antibiotic","-","FALSE","NIL","NO"))
  
  df <- df %>%
    mutate(Antidote.for.Poisons = gsub("\\[|\\]", "", Antidote.for.Poisons)) %>%
    mutate(Antidote.for.Poisons = as.character(Antidote.for.Poisons)) %>%
    mutate(Antidote.for.Poisons = strsplit(Antidote.for.Poisons, ","))
  antidote.for.Poisons <<- colnames(mtabulate(df$Antidote.for.Poisons))
  df <- cbind(df,mtabulate(df$Antidote.for.Poisons))
  df <- df %>% select(-c("Antidote.for.Poisons","-","FALSE","NO"))
}

```

Making the binary dataset
```{r}
redundant_cols <- c("Version","District","hospital.name","Year","Month","Date","Referred.Out.Institute.Name","Reason.For.Referal","Time.of.Arrival","Time.of.first.treatment","Time.of.transfer")
data <- disease_preproc(data, redundant_cols)
#While splitting columns the columns with redundant names like "NIL", "NO","FALSE" manually. Check the preprocessing file with disease_preproc function
```


```{r}
write.csv(data,"/Users/ks/Desktop/DDP/PREM/DATA_27APRIL2020/binarised_data_disease.csv")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

