---
title: "R Notebook"
output: html_notebook
---

Loading Libraries

```{r}
library(plyr)
library(dplyr)
library(tidyverse)
library(cowplot)
library(ggplot2)
library(grid)
library(gridExtra)
library(scales)
library(formattable)
library(cluster)
library(factoextra)
library(qdapTools)
library(reshape2)

```

Load Data
```{r}
data <- read.csv("/Users/ks/Desktop/DDP/PREM/DATA_27APRIL2020/V1_allABCDDF.csv",header=T, na.strings=c("","[]","NA"))
raw <- read.csv("/Users/ks/Desktop/DDP/PREM/DATA_27APRIL2020/raw_data_2019.csv", header=T, na.strings=c("","[]","NA"))
```

Setting default alignment to center
```{r}
theme_update(plot.title = element_text(hjust = 0.5, face = "bold"))
```

Boxplot For Age distribution
```{r}
data$Gender <- as.factor(data$Gender)
data$Age..in.Months. <- as.integer(data$Age..in.Months.)
data %>% 
  filter(!is.na(Gender)) %>%
  filter(!is.na(Age..in.Months.)) %>%
  ggplot(aes(Age..in.Months. , fill = Gender)) + 
  geom_boxplot() + 
  coord_flip() + 
  xlab("Age in Months") + 
  ggtitle("Age Distribution in Raw data")
```

Removing Outliers
```{r}

for (i in 1:length(data$Age..in.Months.)){
    if(is.na(data$Age..in.Months.[i])|| data$Age..in.Months.[i] > 192) {
       (data$Age..in.Months.[i] = NA)
    }
  }
```

Preprocessing
```{r}
source("preprocessing.R")
redundant_cols <- c('X' , 'Unnamed..0' , 'No' , 'X_id' , 'form' , 'owner' , 'Type', 'createdOn', 'Patient.ID' , 'Patient.name', 'Unnamed..71')
col_length <- length(colnames(data))

data <- basic_preproc(data, redundant_cols)
```

Distribution of Age Boxplot
```{r}
data$Gender <- as.factor(data$Gender)
data$Age..in.Months. <- as.integer(data$Age..in.Months.)
#df$Age..in.Months. <- df$Age..in.Months./12
age_box <- data %>% 
            filter(!is.na(Gender)) %>%
            filter(!is.na(Age..in.Months.)) %>%
            ggplot(aes(Age..in.Months. , fill = Gender)) + 
            geom_boxplot(add = "jitter") +
            xlab("Age in Months") + 
             theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size=12, face="bold"),
        plot.margin = unit(c(1, 5.5, 5.5, 20), "points"),  # remove margin on top for better looking co plot
        panel.background = element_rect(fill = "white",  # better grids
                                colour = "white",
                                size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "grey"),
        axis.title.y = element_blank(),
        strip.text.x = element_blank())
age_box
```

Age Distribution Density - Density plot
```{r}
means <- ddply(data, "Gender", summarise, Age.mean = mean(Age..in.Months., na.rm = T))
age_density <- data %>% 
                filter(!is.na(Gender)) %>%
                filter(!is.na(Age..in.Months.)) %>%
                ggplot(aes(Age..in.Months. , fill = Gender)) + 
                geom_density()  +
                geom_vline(data = means, aes(xintercept = Age.mean, colour = Gender),
             linetype = "longdash", size=1) +
                scale_colour_discrete(na.translate = F) +
                
                ggtitle("Age Distribution") +
                xlab("Age in Months") +
                ylab("Density") +
                 theme(legend.position = c(0.95,0.8),   # position inside the plot
        legend.background = element_blank(),  # remove white background blocking grid 
        legend.key.size = unit(0.5, "cm"),  # reduce the size of legend elements
        plot.margin = unit(c(9, 5.5, 2, 20), "points"),  # add top margin, and reduce bottom, makes co plot better
        panel.background = element_rect(fill = "white",
                                colour = "white",
                                size = 0.5, linetype = "solid"),  # better grids
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "grey"),
        axis.title.y = element_blank())

age_density

```

Combined Plot
```{r}
combined_AgeDistribution <- plot_grid(age_density, age_box, align = "v", nrow = 2, rel_heights = c(3/4,1/4))
ggsave("Plots/combined_AgeDistribution.tiff", dpi = 300)
```
```{r}
combined_AgeDistribution

```


Month wise distribution of patients
```{r}
data$Month = as.factor(data$Month)
TotalPatients <- paste("Total Patients:", length(data$Outcome))

Monthwise_Count_bar <- data %>% 
              filter(!is.na(Month)) %>%
              ggplot(aes(x = Month, y = ..count..)) + 
              geom_bar(fill = 'steel blue',width=0.6, position = position_dodge(width=0.2)) +
              labs(x = "Months",
                   y = "Count",
                   title = "Monthwise Patients Count",
                   subtitle = paste0(TotalPatients)) +
              scale_y_continuous(limits = c(0,2500)) +
             theme(plot.subtitle = element_text(hjust = 1, face = "bold.italic"))
 Monthwise_Count_bar
 ggsave("Plots/Monthwise_Count_bar.tiff", dpi = 300)
 
```

District wise distribution of patients
```{r}
districts <- length(unique(data$District))
hospitals <- length(unique(data$hospital.name))
cat('Number of Districts: ', districts)
cat('\nNumber of Hospitals: ', hospitals)
TotalPatients <- paste("Total Patients:", length(data$Outcome))
DistrictwisePatientCount_bar <- data %>%
                  filter(!is.na(District)) %>%
                  ggplot(aes(x = fct_infreq(District), y = ..count..)) +
                  geom_bar(fill = 'steel blue') +
                  labs(x = "Districts",
                       y = "Count",
                       title = "Districtwise Patient Count",
                       subtitle = paste0(TotalPatients)) +
                  theme(axis.text.x = element_text(angle = 90, hjust = 1),
                        plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                        legend.position = c(0.95,0.8),   # position inside the plot
        legend.background = element_blank(),  # remove white background blocking grid 
        legend.key.size = unit(0.2, "cm"),  # reduce the size of legend elements
        plot.margin = unit(c(9, 5.5, 2, 20), "points"),  # add top margin, and reduce bottom, makes co plot better
        axis.title.y = element_blank()) 
                  
DistrictwisePatientCount_bar
ggsave("Plots/DistrictwisePatientCount_bar.tiff", dpi = 300)
```

District wise distribution of patients
```{r}
districts <- length(unique(data$District))
hospitals <- length(unique(data$hospital.name))
cat('Number of Districts: ', districts)
cat('\nNumber of Hospitals: ', hospitals)
TotalPatients <- paste("Total Patients:", length(data$Outcome))
hospital.namewisePatientCount_bar <- data %>%
                  filter(!is.na(hospital.name)) %>%
                  ggplot(aes(x = fct_infreq(hospital.name), y = ..count..)) +
                  geom_bar(fill = 'steel blue') +
                  labs(x = "Hospital names",
                       y = "Count",
                       title = "Hospital wise Patient Count",
                       subtitle = paste0(TotalPatients)) +
                  theme(axis.text.x = element_text(angle = 90, hjust = 1),
                        plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                        legend.position = c(0.95,0.8),   # position inside the plot
        legend.background = element_blank(),  # remove white background blocking grid 
        legend.key.size = unit(0.2, "cm"),  # reduce the size of legend elements
        plot.margin = unit(c(9, 5.5, 2, 20), "points"),  # add top margin, and reduce bottom, makes co plot better
        axis.title.y = element_blank()) 
                  
hospital.namewisePatientCount_bar
ggsave("Plots/hospital.namewisePatientCount_bar.tiff", dpi = 300)
```

Etiology occurences
```{r}
EtiologyCombinations_bar <- data %>% 
                  filter(!is.na(Etiology)) %>%
                  top_n(n = 10) %>%
                  ggplot(aes(x = fct_infreq(Etiology), y = ..count..)) + 
                  geom_bar(fill = 'steel blue') +
                  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                  xlab('Etiology') +
                  ylab("Count") +
                  ggtitle("Etiology Combinations Count")

EtiologyCombinations_bar
ggsave("Plots/EtiologyCombinations_bar.jpg",dpi = 300)
```

Monthwise entries in Districts
```{r}
monthwise_districts <- data %>% 
                       select(c(Month, District)) %>%
                       filter(!is.na(District)) %>%
                       filter(!is.na(Month)) 
monthwise_districts <- cbind(monthwise_districts, mtabulate(monthwise_districts$District)) %>%
                       select(-c(District)) %>%
                       group_by(Month) %>%
                       summarise_all(funs(sum)) %>%
                       melt(id = "Month") %>%
                       mutate(Month = as.integer(Month)) %>%
                       mutate(value = as.numeric(value))
  
ggplot(data=monthwise_districts,
       aes(x=Month, y=value, colour=variable)) +
       geom_point()+
       geom_line() + 
       ylab('')+
       scale_x_continuous(breaks=c(1:12))

ggsave("Plots/DistrictandMonth.tiff", dpi = 300)
```

Death Rates in districts
```{r}
overall_deaths <- length(which(data$Outcome == 'Died'))
cat('Overall Death Percent:', 100*(overall_deaths/length(data$Outcome)),"%")

a <- data %>%
        group_by(District, Outcome) %>%
        summarise(total = length(Outcome))

b <- a %>% 
      group_by(District) %>%
      summarise(Total = sum(total)) 
    
c <- subset(a , a$Outcome == 'Died')
d = inner_join(b,c, by = 'District')
d <- d %>% 
      rename_at("total",~"Died") %>%  
      select(-Outcome) %>% 
      mutate(Rate =100*(Died/Total)) %>%
      arrange(desc(Rate))
d$Rate = formattable(d$Rate, digits = 2, format = "f")
TotalDeaths <- paste("Total Deaths: ", sum(d$Died))
DeathRates_districtwise <- d %>%
                              filter(Total > 50) %>%  #removing districts with 50 or fewwer 
                              ggplot(aes(x = reorder(District,-Rate), y= Rate)) +
                              geom_bar(stat= "identity", fill = "steel blue") +
                              theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                              geom_text(aes(label=Rate), position=position_dodge(width=0.9), vjust=-0.25) +
                              labs(x = "Districts",
                                   y = '% Death Rate',
                                   title = "Death Rate",
                                   subtitle = paste0(TotalDeaths)) + 
                              theme(panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    axis.line = element_line(size = 0.5, linetype = "solid",colour = "black"),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"))
DeathRates_districtwise
ggsave("Plots/DeathRates_districtwise.tiff", dpi = 300)


```

Referred Out Rates District
```{r}
overall_deaths <- length(which(data$Outcome == 'ReferredOut'))
cat('Overall Referred Out Percent:', 100*(overall_deaths/length(data$Outcome)),"%")

a <- data %>%
        group_by(District, Outcome) %>%
        summarise(total = length(Outcome))

b <- a %>% 
      group_by(District) %>%
      summarise(Total = sum(total)) 
    
c <- subset(a , a$Outcome == 'ReferredOut')
d = inner_join(b,c, by = 'District')
d <- d %>% 
      rename_at("total",~"ReferredOut") %>%  
      select(-Outcome) %>% 
      mutate(Rate =100*(ReferredOut/Total)) %>%
      arrange(desc(Rate))
d$Rate = formattable(d$Rate, digits = 2, format = "f")

TotalReferredOut = paste("Total Referred Outs: ", sum(d$ReferredOut))
RefferedOutRates_districtwise <- d %>%
                              filter(Total > 50) %>%  #removing districts with 10 or fewwer 
                              ggplot(aes(x = reorder(District,-Rate), y= Rate)) +
                              geom_bar(stat= "identity", fill = "steel blue") +
                              theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                              geom_text(aes(label=Rate), position=position_dodge(width=0.9), vjust=-0.25, size = 3) +
                              labs(x = "Districts",
                                   y = "% Referred Out Rate",
                                   title = "Referred Out Rate - Districtwise",
                                   subtitle = paste0(TotalReferredOut)) + 
                              theme(panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                                    axis.line = element_line(size = 0.5, linetype = "solid",colour = "black"))
RefferedOutRates_districtwise
ggsave("Plots/RefferedOutRates_districtwise.tiff", dpi = 300)


```

Referred Out Rates Hospital Wise

```{r}
overall_deaths <- length(which(data$Outcome == 'ReferredOut'))
cat('Overall Referred Out Percent:', 100*(overall_deaths/length(data$Outcome)),"%")

a <- data %>%
        group_by(hospital.name, Outcome) %>%
        summarise(total = length(Outcome))

b <- a %>% 
      group_by(hospital.name) %>%
      summarise(Total = sum(total)) 
    
c <- subset(a , a$Outcome == 'ReferredOut')
d = inner_join(b,c, by = 'hospital.name')
d <- d %>% 
      rename_at("total",~"ReferredOut") %>%  
      select(-Outcome) %>% 
      mutate(Rate =100*(ReferredOut/Total)) %>%
      arrange(desc(Rate))
d$Rate = formattable(d$Rate, digits = 2, format = "f")

TotalReferredOut = paste("Total Referred Outs: ", sum(d$ReferredOut))
RefferedOutRates_hospital.namewise <- d %>%
                              filter(Total > 50) %>%  #removing hospital.names with 10 or fewwer 
                              ggplot(aes(x = reorder(hospital.name,-Rate), y= Rate)) +
                              geom_bar(stat= "identity", fill = "steel blue") +
                              theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                              geom_text(aes(label=Rate), position=position_dodge(width=0.9), vjust=-0.25, size = 3) +
                              labs(x = "Hospitals",
                                   y = "% Referred Out Rate",
                                   title = "Referred Out Rate - Hospitalwise",
                                   subtitle = paste0(TotalReferredOut)) + 
                              theme(panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                                    axis.line = element_line(size = 0.5, linetype = "solid",colour = "black"))
RefferedOutRates_hospital.namewise
ggsave("Plots/RefferedOutRates_hospital.namewise.tiff", dpi = 300)



```



ROut Rate With only Assesment - District
```{r}
overall_deaths <- length(which(data$Outcome == 'ReferredOut'))
cat('Overall Referred Out Percent:', 100*(overall_deaths/length(data$Outcome)),"%")


noNArowsABCD_idx <- raw %>% 
                  select(c("Airway","Breathing","Circulation","Disability")) %>%
                  is.na() %>%
                  apply(MARGIN = 1, function(x) any(x %in% FALSE))

onlyNArowsTRT_idx <- raw[noNArowsABCD_idx,] %>%
                  select(c("Head.Tilt.Chin.Lift" ,"Bag.valve.Mask.Ventilation","CPAP", "Intubation", "Bronchodialators", "Cardiac.Massage", "Normal.Saline.Bolus", "Inotrope", "X25..Dextrose","CSstabilization", "Anti.Fit.Medication")) %>%
                  is.na() %>%
                  apply(MARGIN = 1, FUN = all)

treat_na = raw[onlyNArowsTRT_idx,]
a <- treat_na %>%
        group_by(District, Outcome) %>%
        summarise(total = length(Outcome))

b <- a %>% 
      group_by(District) %>%
      summarise(Total = sum(total)) 
    
c <- subset(a , a$Outcome == 'ReferredOut')
d = inner_join(b,c, by = 'District')
d <- d %>% 
      rename_at("total",~"ReferredOut") %>%  
      select(-Outcome) %>% 
      mutate(Rate =100*(ReferredOut/Total)) %>%
      arrange(desc(Rate))
d$Rate = formattable(d$Rate, digits = 2, format = "f")

TotalReferredOut = paste("Total Referred Outs with only Assesment: ", sum(d$ReferredOut))
RefferedOutRates_onlyAssesment<- d %>%
                              filter(Total > 50) %>%  #removing districts with 50 or fewwer 
                              ggplot(aes(x = reorder(District,-Rate), y= Rate)) +
                              geom_bar(stat= "identity", fill = "steel blue") +
                              theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                              geom_text(aes(label=Rate), position=position_dodge(width=0.9), vjust=-0.25, size = 3) +
                              labs(x = "Districts",
                                   y = "% Referred Out Rate",
                                   title = "ROut Rate With only Assesment - Districts",
                                   subtitle = paste0(TotalReferredOut)) + 
                              theme(panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                                    axis.line = element_line(size = 0.5, linetype = "solid",colour = "black"))

RefferedOutRates_onlyAssesment
ggsave("Plots/ROut Rate With only Assesment.jpg", dpi = 300)
write.csv(d, "/Users/ks/Desktop/DDP/PREM/Analysis/ReferredOut/OnlyAssesment_Districts.csv", row.names = FALSE)

```

ROut Rate With only Assesment - Hospital
```{r}
overall_deaths <- length(which(data$Outcome == 'ReferredOut'))
cat('Overall Referred Out Percent:', 100*(overall_deaths/length(data$Outcome)),"%")


noNArowsABCD_idx <- raw %>% 
                  select(c("Airway","Breathing","Circulation","Disability")) %>%
                  is.na() %>%
                  apply(MARGIN = 1, function(x) any(x %in% FALSE))

onlyNArowsTRT_idx <- raw[noNArowsABCD_idx,] %>%
                  select(c("Head.Tilt.Chin.Lift" ,"Bag.valve.Mask.Ventilation","CPAP", "Intubation", "Bronchodialators", "Cardiac.Massage", "Normal.Saline.Bolus", "Inotrope", "X25..Dextrose","CSstabilization", "Anti.Fit.Medication")) %>%
                  is.na() %>%
                  apply(MARGIN = 1, FUN = all)

treat_na = raw[onlyNArowsTRT_idx,]
a <- treat_na %>%
        group_by(hospital.name, Outcome) %>%
        summarise(total = length(Outcome))

b <- a %>% 
      group_by(hospital.name) %>%
      summarise(Total = sum(total)) 
    
c <- subset(a , a$Outcome == 'ReferredOut')
d = inner_join(b,c, by = 'hospital.name')
d <- d %>% 
      rename_at("total",~"ReferredOut") %>%  
      select(-Outcome) %>% 
      mutate(Rate =100*(ReferredOut/Total)) %>%
      arrange(desc(Rate))
d$Rate = formattable(d$Rate, digits = 2, format = "f")

TotalReferredOut = paste("Total Referred Outs with only Assesment: ", sum(d$ReferredOut))
RefferedOutRates_onlyAssesment<- d %>%
                              filter(Total > 50) %>%  #removing hospital.names with 50 or fewwer 
                              ggplot(aes(x = reorder(hospital.name,-Rate), y= Rate)) +
                              geom_bar(stat= "identity", fill = "steel blue") +
                              theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                              geom_text(aes(label=Rate), position=position_dodge(width=0.9), vjust=-0.25, size = 3) +
                              labs(x = "Hospitals",
                                   y = "% Referred Out Rate",
                                   title = "ROut Rate With only Assesment -Hospital",
                                   subtitle = paste0(TotalReferredOut)) + 
                              theme(panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                                    axis.line = element_line(size = 0.5, linetype = "solid",colour = "black"))

RefferedOutRates_onlyAssesment
ggsave("Plots/ROut Rate With only Assesment.jpg", dpi = 300)
write.csv(d, "/Users/ks/Desktop/DDP/PREM/Analysis/ReferredOut/OnlyAssesment_Hospitals.csv", row.names = FALSE)

```

ROut without Assesment - District
```{r}
overall_deaths <- length(which(raw$Outcome == 'ReferredOut'))
cat('Overall Referred Out Percent:', 100*(overall_deaths/length(raw$Outcome)),"%")


onlyNArows_idx <- raw %>% 
                  select(c("Airway","Breathing","Circulation","Disability")) %>%
                  is.na() %>%
                  apply(MARGIN = 1, function(x) any(x %in% TRUE))


treat_na = raw[onlyNArows_idx,]
a <- treat_na %>%
        group_by(District, Outcome) %>%
        summarise(total = length(Outcome))

b <- a %>% 
      group_by(District) %>%
      summarise(Total = sum(total)) 
    
c <- subset(a , a$Outcome == 'ReferredOut')
d = inner_join(b,c, by = 'District')
d <- d %>% 
      rename_at("total",~"ReferredOut") %>%  
      select(-Outcome) %>% 
      mutate(Rate =100*(ReferredOut/Total)) %>%
      arrange(desc(Rate))
d$Rate = formattable(d$Rate, digits = 2, format = "f")

TotalReferredOut = paste("Total Referred Outs without Assesment: ", sum(d$ReferredOut))
RefferedOutRates_WOAssesment<- d %>%
                              filter(Total > 50) %>%  #removing districts with 50 or fewwer 
                              ggplot(aes(x = reorder(District,-Rate), y= Rate)) +
                              geom_bar(stat= "identity", fill = "steel blue") +
                              theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                              geom_text(aes(label=Rate), position=position_dodge(width=0.9), vjust=-0.25, size = 3) +
                              labs(x = "Districts",
                                   y = "% Referred Out Rate",
                                   title = "ROut Rate without Assesment - District",
                                   subtitle = paste0(TotalReferredOut)) + 
                              theme(panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                                    axis.line = element_line(size = 0.5, linetype = "solid",colour = "black"))

RefferedOutRates_WOAssesment
ggsave("Plots/ROut without Assesment.jpg", dpi = 300)
write.csv(d, "/Users/ks/Desktop/DDP/PREM/Analysis/ReferredOut/WOAssesment_District.csv", row.names = FALSE)

```

ROut without Assesment - Hospitals
```{r}
overall_deaths <- length(which(raw$Outcome == 'ReferredOut'))
cat('Overall Referred Out Percent:', 100*(overall_deaths/length(raw$Outcome)),"%")


onlyNArows_idx <- raw %>% 
                  select(c("Airway","Breathing","Circulation","Disability")) %>%
                  is.na() %>%
                  apply(MARGIN = 1, function(x) any(x %in% TRUE))


treat_na = raw[onlyNArows_idx,]
a <- treat_na %>%
        group_by(hospital.name, Outcome) %>%
        summarise(total = length(Outcome))

b <- a %>% 
      group_by(hospital.name) %>%
      summarise(Total = sum(total)) 
    
c <- subset(a , a$Outcome == 'ReferredOut')
d = inner_join(b,c, by = 'hospital.name')
d <- d %>% 
      rename_at("total",~"ReferredOut") %>%  
      select(-Outcome) %>% 
      mutate(Rate =100*(ReferredOut/Total)) %>%
      arrange(desc(Rate))
d$Rate = formattable(d$Rate, digits = 2, format = "f")

TotalReferredOut = paste("Total Referred Outs without Assesment: ", sum(d$ReferredOut))
RefferedOutRates_WOAssesment<- d %>%
                              filter(Total > 50) %>%  #removing hospital.names with 50 or fewwer 
                              ggplot(aes(x = reorder(hospital.name,-Rate), y= Rate)) +
                              geom_bar(stat= "identity", fill = "steel blue") +
                              theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                              geom_text(aes(label=Rate), position=position_dodge(width=0.9), vjust=-0.25, size = 3) +
                              labs(x = "Hospitals",
                                   y = "% Referred Out Rate",
                                   title = "ROut Rate without Assesment - Hospitals",
                                   subtitle = paste0(TotalReferredOut)) + 
                              theme(panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                                    axis.line = element_line(size = 0.5, linetype = "solid",colour = "black"))

RefferedOutRates_WOAssesment
ggsave("Plots/ROut without Assesment.jpg", dpi = 300)
write.csv(d, "/Users/ks/Desktop/DDP/PREM/Analysis/ReferredOut/WOAssesment_hospitals.csv", row.names = FALSE)

```

Referred Out without both Assesment and treatment - District
```{r}
overall_deaths <- length(which(raw$Outcome == 'ReferredOut'))
cat('Overall Referred Out Percent:', 100*(overall_deaths/length(raw$Outcome)),"%")


onlyNArowsABCD_idx <- raw %>% 
                  select(c("Airway","Breathing","Circulation","Disability")) %>%
                  is.na() %>%
                  apply(MARGIN = 1, function(x) any(x %in% TRUE))

onlyNArows_idx <- raw[onlyNArowsABCD_idx,] %>%
                  select(c("Head.Tilt.Chin.Lift" ,"Bag.valve.Mask.Ventilation","CPAP", "Intubation", "Bronchodialators", "Cardiac.Massage", "Normal.Saline.Bolus", "Inotrope", "X25..Dextrose","CSstabilization", "Anti.Fit.Medication")) %>%
                  is.na() %>%
                  apply(MARGIN = 1, FUN = all)


treat_na = raw[onlyNArows_idx,]
a <- treat_na %>%
        group_by(District, Outcome) %>%
        summarise(total = length(Outcome))

b <- a %>% 
      group_by(District) %>%
      summarise(Total = sum(total)) 
    
c <- subset(a , a$Outcome == 'ReferredOut')
d = inner_join(b,c, by = 'District')
d <- d %>% 
      rename_at("total",~"ReferredOut") %>%  
      select(-Outcome) %>% 
      mutate(Rate =100*(ReferredOut/Total)) %>%
      arrange(desc(Rate))
d$Rate = formattable(d$Rate, digits = 2, format = "f")

TotalReferredOut = paste("Total(on raw data): ", sum(d$ReferredOut))
RefferedOutRates_WOAssesmentandTRT<- d %>%
                              filter(Total > 50) %>%  #removing districts with 50 or fewwer 
                              ggplot(aes(x = reorder(District,-Rate), y= Rate)) +
                              geom_bar(stat= "identity", fill = "steel blue") +
                              theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                              geom_text(aes(label=Rate), position=position_dodge(width=0.9), vjust=-0.25, size = 3) +
                              labs(x = "Districts",
                                   y = "% Referred Out Rate",
                                   title = "ROut Rate without Assesment and Treatment",
                                   subtitle = paste0(TotalReferredOut)) + 
                              theme(axis.text.x = element_text(size = 10),
                                    panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                                    axis.line = element_line(size = 0.5, linetype = "solid",colour = "black"))

RefferedOutRates_WOAssesmentandTRT
ggsave("Plots/ROut without Assesment and Treatment.tiff", dpi = 300)
write.csv(d, "/Users/ks/Desktop/DDP/PREM/Analysis/ReferredOut/WOAssesmentandTreatment_District.csv", row.names = FALSE)


```

Referred Out without both Assesment and treatment - Hospital
```{r}
overall_deaths <- length(which(raw$Outcome == 'ReferredOut'))
cat('Overall Referred Out Percent:', 100*(overall_deaths/length(raw$Outcome)),"%")


onlyNArowsABCD_idx <- raw %>% 
                  select(c("Airway","Breathing","Circulation","Disability")) %>%
                  is.na() %>%
                  apply(MARGIN = 1, function(x) any(x %in% TRUE))

onlyNArows_idx <- raw[onlyNArowsABCD_idx,] %>%
                  select(c("Head.Tilt.Chin.Lift" ,"Bag.valve.Mask.Ventilation","CPAP", "Intubation", "Bronchodialators", "Cardiac.Massage", "Normal.Saline.Bolus", "Inotrope", "X25..Dextrose","CSstabilization", "Anti.Fit.Medication")) %>%
                  is.na() %>%
                  apply(MARGIN = 1, FUN = all)


treat_na = raw[onlyNArows_idx,]
a <- treat_na %>%
        group_by(hospital.name, Outcome) %>%
        summarise(total = length(Outcome))

b <- a %>% 
      group_by(hospital.name) %>%
      summarise(Total = sum(total)) 
    
c <- subset(a , a$Outcome == 'ReferredOut')
d = inner_join(b,c, by = 'hospital.name')
d <- d %>% 
      rename_at("total",~"ReferredOut") %>%  
      select(-Outcome) %>% 
      mutate(Rate =100*(ReferredOut/Total)) %>%
      arrange(desc(Rate))
d$Rate = formattable(d$Rate, digits = 2, format = "f")

TotalReferredOut = paste("Total Referred Outs without Assesment and Treatment: ", sum(d$ReferredOut))
RefferedOutRates_WOAssesmentandTRT<- d %>%
                              filter(Total > 50) %>%  #removing hospital.names with 50 or fewwer 
                              ggplot(aes(x = reorder(hospital.name,-Rate), y= Rate)) +
                              geom_bar(stat= "identity", fill = "steel blue") +
                              theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                              geom_text(aes(label=Rate), position=position_dodge(width=0.9), vjust=-0.25, size = 3) +
                              labs(x = "Hospitals",
                                   y = "% Referred Out Rate",
                                   title = "ROut Rate without Assesment and Treatment - Hospital",
                                   subtitle = paste0(TotalReferredOut)) + 
                              theme(panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                                    axis.line = element_line(size = 0.5, linetype = "solid",colour = "black"))

RefferedOutRates_WOAssesmentandTRT
ggsave("Plots/ROut without Assesment and Treatment.jpg", dpi = 300)
write.csv(d, "/Users/ks/Desktop/DDP/PREM/Analysis/ReferredOut/WOAssesmentandTreatment_hospital.name.csv", row.names = FALSE)


```

Preprocessing into binarised data
```{r}
redundant_cols <- c("Version","District","hospital.name","Year","Month","Date","Referred.Out.Institute.Name","Reason.For.Referal","Time.of.Arrival","Time.of.first.treatment","Time.of.transfer")
binarised_data <- disease_preproc(data, redundant_cols)

```


Etiology Combinations
```{r}
combination_etiology <- data.frame(matrix(ncol=2,nrow=0, dimnames=list(NULL, c("Etiology Combinations", "Frequency"))))
combination_etiology <- combination_etiology %>%
                            mutate(Etiology.Combinations = as.character(Etiology.Combinations)) %>%
                            mutate(Frequency = as.integer(Frequency))
for (i in 1:length(etiology)) {
  for (j in i:length(etiology)) {
    t <- table(etiology[,i], etiology[,j])
    
    if(names(etiology)[i] != names(etiology)[j]) {
       cmb<- c(names(etiology)[i], names(etiology)[j])
       cmb<- paste(cmb, collapse = ", ")
       if(t[4] > 50){combination_etiology <- combination_etiology %>% add_row(Etiology.Combinations = cmb, Frequency = t[4])}
    } else{
    if(t[4] > 50){combination_etiology <- combination_etiology %>% add_row(Etiology.Combinations = names(etiology)[i], Frequency = t[4])}
    }
  }
}
```

Etiology Combinations Plot
```{r}
theme_update(plot.title = element_text(hjust = 0.5, face = "bold"))


etiology_combinations_bar <- combination_etiology %>% top_n(20, Frequency) %>%
                                    ggplot(aes(x = reorder(Etiology.Combinations,-Frequency) ,y=Frequency)) + 
                                    
                                    geom_bar(stat = "identity", fill = 'steel blue') +
  
                                    theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
                              labs(x = "Etiology",
                                   y = "Count",
                                   title = "Etiology Combinations") + 
                              theme(panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                                    axis.line = element_line(size = 0.5, linetype = "solid", colour = "black")) 
etiology_combinations_bar
```

Monthwise Etiology
```{r}
monthwise_etiology <- binarised_data %>%
                      select(c(colnames(etiology))) %>%
                      cbind(data$Month) %>%
                      rename(Month = `data$Month`) %>%
                      group_by(Month) %>%
                      summarise_all(funs(sum))

meMelt <- melt(monthwise_etiology) %>% 
          arrange(desc(value)) %>%
          group_by(Month) %>%
          slice(1:4)

monthwise_etiology_plot <- meMelt %>% 
                           ggplot(aes(x = variable,y = value)) + 
                  geom_bar(aes(fill = variable),stat = "identity",position = "dodge") +                   facet_wrap(~Month, ncol = 6) +
                  theme(axis.text.x = element_blank()) + 
                              labs(x = "Etiology",
                                   y = "Count",
                                   title = "Top etiologies - Monthwise") + 
                              theme(aspect.ratio = 1,
                                    panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    legend.position = "bottom",
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                                    axis.line = element_line(size = 0.5, linetype = "solid", colour = "black")) 
ggsave("Plots/topEtiologies_Monthwise.tiff", dpi = 300)
monthwise_etiology_plot
```

Fever over the months
```{r}
monthwise_Fever <- binarised_data %>%
                   cbind(data$Month, data$District) %>%
                   rename(Month = `data$Month`) %>%
                   group_by(Month) %>%
                   summarise(Fever = sum(Fever))

monthwise_Fever_plot <- monthwise_Fever %>%
                        ggplot(aes(x = Month, y= Fever)) + 
                        geom_bar(stat = "identity", fill = 'steel blue',width=0.6, position = position_dodge(width=0.2)) + 
                        labs(title = "Fever Monthwise")
                        

monthwise_Fever_plot
```

```{r}
combined_patients_Fever <- plot_grid(monthwise_Fever_plot, Monthwise_Count_bar, align = "v", nrow = 2, rel_heights = c(1/2,2/3))
combined_patients_Fever
ggsave("Plots/combined_monthwise_feverandOverall.tiff", dpi = 300)

```

Breathlessness over the months
```{r}
monthwise_Breathlessness <- binarised_data %>%
                   cbind(data$Month, data$District) %>%
                   rename(Month = `data$Month`) %>%
                   group_by(Month) %>%
                   summarise(Breathlessness = sum(Breathlessness))

monthwise_Breathlessness_plot <- monthwise_Breathlessness %>%
                        ggplot(aes(x = Month, y= Breathlessness)) + 
                        geom_bar(stat = "identity", fill = 'steel blue',width=0.6, position = position_dodge(width=0.2)) + 
                        labs(title = "Breathlessness Combinations")
                        

monthwise_Breathlessness_plot
```

```{r}
combined_patients_breathlessness <- plot_grid(monthwise_Breathlessness_plot, Monthwise_Count_bar, align = "v", nrow = 2, rel_heights = c(1/2,2/3))
combined_patients_breathlessness

```

ABCD Combinations
```{r}
ABCD_combinations <- data %>% 
                            count(Airway, Breathing, Circulation, Disability)
cat("Number of unique combinations: ", nrow(ABCD_combinations))
ABCD_combinations <- ABCD_combinations %>%
                        arrange(desc(n))
a = head(ABCD_combinations,10)
write.csv(a, "/Users/ks/Desktop/DDP/PREM/Analysis/ABCD_combinations.csv")
```


```{r}

```

