---
title: "R Notebook"
output: html_notebook
---

Loading Libraries

```{r}
library(dplyr)
library(tidyverse)
library(cowplot)
library(ggplot2)
library(grid)
library(gridExtra)
library(scales)
library(formattable)
```

Load Data
```{r}
data <- read.csv("/Users/ks/Desktop/DDP/PREM/DATA_27APRIL2020/V1_allABCDDF.csv",header=T, na.strings=c("","[]","NA"))

```

Setting default alignment to center
```{r}
theme_update(plot.title = element_text(hjust = 0.5, face = "bold"))
```

Boxplot For Age distribution
```{r}
data$Gender <- as.factor(data$Gender)
data$Age..in.Months. <- as.integer(data$Age..in.Months.)
data %>% 
  filter(!is.na(Gender)) %>%
  filter(!is.na(Age..in.Months.)) %>%
  ggplot(aes(Age..in.Months. , fill = Gender)) + 
  geom_boxplot() + 
  coord_flip() + 
  xlab("Age in Months") + 
  ggtitle("Age Distribution in Raw data")
```

Removing Outliers
```{r}

for (i in 1:length(data$Age..in.Months.)){
    if(is.na(data$Age..in.Months.[i])|| data$Age..in.Months.[i] > 192) {
       (data$Age..in.Months.[i] = NA)
    }
  }
```

Preprocessing
```{r}
source("preprocessing.R")
redundant_cols <- c('X' , 'Unnamed..0' , 'No' , 'X_id' , 'form' , 'owner' , 'Type', 'createdOn', 'Patient.ID' , 'Patient.name', 'Unnamed..71')
col_length <- length(colnames(data))

data <- basic_preproc(data, redundant_cols)
```

Distribution of Age Boxplot
```{r}
data$Gender <- as.factor(data$Gender)
data$Age..in.Months. <- as.integer(data$Age..in.Months.)
#df$Age..in.Months. <- df$Age..in.Months./12
age_box <- data %>% 
            filter(!is.na(Gender)) %>%
            filter(!is.na(Age..in.Months.)) %>%
            ggplot(aes(Age..in.Months. , fill = Gender)) + 
            geom_boxplot(add = "jitter") +
            xlab("Age in Months") + 
             theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size=12, face="bold"),
        plot.margin = unit(c(1, 5.5, 5.5, 20), "points"),  # remove margin on top for better looking co plot
        panel.background = element_rect(fill = "white",  # better grids
                                colour = "white",
                                size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "grey"),
        axis.title.y = element_blank(),
        strip.text.x = element_blank())
age_box
```

Age Distribution Density - Density plot
```{r}
age_density <- data %>% 
                filter(!is.na(Gender)) %>%
                filter(!is.na(Age..in.Months.)) %>%
                ggplot(aes(Age..in.Months. , fill = Gender)) + 
                geom_density() +
                ggtitle("Age Distribution") +
                xlab("") +
                ylab("Density") +
                 theme(legend.position = c(0.95,0.8),   # position inside the plot
        legend.background = element_blank(),  # remove white background blocking grid 
        legend.key.size = unit(0.8, "cm"),  # reduce the size of legend elements
        plot.margin = unit(c(9, 5.5, 2, 20), "points"),  # add top margin, and reduce bottom, makes co plot better
        panel.background = element_rect(fill = "white",
                                colour = "white",
                                size = 0.5, linetype = "solid"),  # better grids
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "grey"),
        axis.title.y = element_blank())

age_density

```

Combined Plot
```{r}
combined_AgeDistribution <- plot_grid(age_density, age_box, align = "v", nrow = 2, rel_heights = c(3/4,1/4))
ggsave("Plots/combined_AgeDistribution.jpg", dpi = 300)
```
```{r}
combined_AgeDistribution

```


Month wise distribution of patients
```{r}
data$Month = as.factor(data$Month)
TotalPatients <- paste("Total Patients:", length(data$Outcome))

Monthwise_Count_bar <- data %>% 
              filter(!is.na(Month)) %>%
              ggplot(aes(x = Month, y = ..count..)) + 
              geom_bar(fill = 'steel blue') +
              labs(x = "Months",
                   y = "Count",
                   title = "Monthwise Patients Count",
                   subtitle = paste0(TotalPatients)) +
              scale_y_continuous(limits = c(0,2500)) +
             theme(plot.subtitle = element_text(hjust = 1, face = "bold.italic"),legend.position = c(0.95,0.8),   # position inside the plot
        legend.background = element_blank(),  # remove white background blocking grid 
        legend.key.size = unit(0.2, "cm"),  # reduce the size of legend elements
        plot.margin = unit(c(9, 5.5, 2, 20), "points"),  # add top margin, and reduce bottom, makes co plot better
        panel.background = element_rect(fill = "white",
                                colour = "white",
                                size = 0.5, linetype = "solid"),  # better grids
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "grey"),
        axis.title.y = element_blank())
 Monthwise_Count_bar
 ggsave("Plots/Monthwise_Count_bar.jpg", dpi = 300)
 
```

District wise distribution of patients
```{r}
districts <- length(unique(data$District))
hospitals <- length(unique(data$hospital.name))
cat('Number of Districts: ', districts)
cat('\nNumber of Hospitals: ', hospitals)
TotalPatients <- paste("Total Patients:", length(data$Outcome))
DistrictwisePatientCount_bar <- data %>%
                  filter(!is.na(District)) %>%
                  ggplot(aes(x = fct_infreq(District), y = ..count..)) +
                  geom_bar(fill = 'steel blue') +
                  labs(x = "Districts",
                       y = "Count",
                       title = "Districtwise Patient Count",
                       subtitle = paste0(TotalPatients)) +
                  theme(axis.text.x = element_text(angle = 90, hjust = 1),
                        plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                        legend.position = c(0.95,0.8),   # position inside the plot
        legend.background = element_blank(),  # remove white background blocking grid 
        legend.key.size = unit(0.2, "cm"),  # reduce the size of legend elements
        plot.margin = unit(c(9, 5.5, 2, 20), "points"),  # add top margin, and reduce bottom, makes co plot better
        panel.background = element_rect(fill = "white",
                                colour = "white",
                                size = 0.5, linetype = "solid"),  # better grids
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "grey"),
        axis.title.y = element_blank()
                        ) 
                  
DistrictwisePatientCount_bar
ggsave("Plots/DistrictwisePatientCount_bar.jpg", dpi = 300)
```

Etiology occurences
```{r}
EtiologyCombinations_bar <- data %>% 
                  filter(!is.na(Etiology)) %>%
                  top_n(n = 10) %>%
                  ggplot(aes(x = fct_infreq(Etiology), y = ..count..)) + 
                  geom_bar(fill = 'steel blue') +
                  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                  xlab('Etiology') +
                  ylab("Count") +
                  ggtitle("Etiology Combinations Count")

EtiologyCombinations_bar
ggsave("Plots/EtiologyCombinations_bar.jpg",dpi = 300)
```

Death Rates in districts
```{r}
overall_deaths <- length(which(data$Outcome == 'Died'))
cat('Overall Death Percent:', 100*(overall_deaths/length(data$Outcome)),"%")

a <- data %>%
        group_by(District, Outcome) %>%
        summarise(total = length(Outcome))

b <- a %>% 
      group_by(District) %>%
      summarise(Total = sum(total)) 
    
c <- subset(a , a$Outcome == 'Died')
d = inner_join(b,c, by = 'District')
d <- d %>% 
      rename_at("total",~"Died") %>%  
      select(-Outcome) %>% 
      mutate(Rate =100*(Died/Total)) %>%
      arrange(desc(Rate))
d$Rate = formattable(d$Rate, digits = 2, format = "f")
TotalDeaths <- paste("Total Deaths: ", sum(d$Died))
DeathRates_districtwise <- d %>%
                              filter(Total > 50) %>%  #removing districts with 10 or fewwer 
                              ggplot(aes(x = reorder(District,-Rate), y= Rate)) +
                              geom_bar(stat= "identity", fill = "steel blue") +
                              theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                              geom_text(aes(label=Rate), position=position_dodge(width=0.9), vjust=-0.25) +
                              labs(x = "Districts",
                                   y = '% Death Rate',
                                   title = "Death Rate - Districtwise",
                                   subtitle = paste0(TotalDeaths)) + 
                              theme(panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    axis.line = element_line(size = 0.5, linetype = "solid",colour = "black"),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"))
DeathRates_districtwise
ggsave("Plots/DeathRates_districtwise.jpg", dpi = 300)


```

Referred Out Rates
```{r}
overall_deaths <- length(which(data$Outcome == 'Died'))
cat('Overall Death Percent:', 100*(overall_deaths/length(data$Outcome)),"%")

a <- data %>%
        group_by(District, Outcome) %>%
        summarise(total = length(Outcome))

b <- a %>% 
      group_by(District) %>%
      summarise(Total = sum(total)) 
    
c <- subset(a , a$Outcome == 'ReferredOut')
d = inner_join(b,c, by = 'District')
d <- d %>% 
      rename_at("total",~"ReferredOut") %>%  
      select(-Outcome) %>% 
      mutate(Rate =100*(ReferredOut/Total)) %>%
      arrange(desc(Rate))
d$Rate = formattable(d$Rate, digits = 2, format = "f")

TotalReferredOut = paste("Total Referred Outs: ", sum(d$ReferredOut))
RefferedOutRates_districtwise <- d %>%
                              filter(Total > 50) %>%  #removing districts with 10 or fewwer 
                              ggplot(aes(x = reorder(District,-Rate), y= Rate)) +
                              geom_bar(stat= "identity", fill = "steel blue") +
                              theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
                              geom_text(aes(label=Rate), position=position_dodge(width=0.9), vjust=-0.25, size = 3) +
                              labs(x = "Districts",
                                   y = "% Referred Out Rate",
                                   title = "Referred Out Rate - Districtwise",
                                   subtitle = paste0(TotalReferredOut)) + 
                              theme(panel.border = element_blank(),
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(),
                                    plot.subtitle = element_text(hjust = 1, face = "bold.italic"),
                                    axis.line = element_line(size = 0.5, linetype = "solid",colour = "black"))
RefferedOutRates_districtwise
ggsave("Plots/RefferedOutRates_districtwise.jpg", dpi = 300)


```

Saving Plots
```{r}


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

